Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-17 chapters/introduction/introduction.tex
geo-calibration feature learning

Automatic feature engineering has drawn a lot of attention over the
past years in the computer vision community due to its efficiency and
not requiring expert knowledge about the data. Deep neural networks
are wildly accepted by researchers as good tools to learn high-level
image representations.
The most commonly used approach for deep feature learning is
full supervision, which usually requires manually annotated
data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Though full supervision work well in many applications, there are
exponentially more image resources without manual annotation (cell
phone imagery, YouTube videos\etc), which show a huge potential for
visual feature learning.

To exploit these unlabeled data, recent work has explored the use of
self-supervision (sometimes referred to as unsupervised learning or
pretext tasks) for training deep neural networks that capture useful
visual representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data (e.g., pixel color values) to
avoid expensive manual annotation. As a byproduct, a useful visual
representation is learned.
For example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As new learning technique address the lack of massive amounts of
labeled data, domain adaptation adapt the feature generating model to
another feature domain so that it improve the performance when dealing
with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} proposed to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabled video imagery.

%\section{\todo{Dataset}}
%Introduce the dataset we use.

>>>>

Automatic feature engineering has drawn a lot of attention over the
past years due to its ability to learn useful features without strong
expert knowledge about the data. Among many automatic feature
engineering approaches, deep neural networks are wildly accepted by
researchers as good tools to learn high-level image representations.
The most commonly used approach for deep feature learning is
full supervision, which usually requires manually annotated
data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks. 
In contrast, unlabeled data is offen plentiful (\ie cellphone photos
in Instagram or Youtube videos).

To exploit these unlabeled data, recent work has explored
self-supervision methods (sometimes referred to as unsupervised learning or
pretext tasks) for training deep neural networks that capture useful
visual representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data (e.g., pixel color values) to
avoid expensive manual annotation. As a byproduct, a useful visual
representation is learned.
For example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As new learning technique address the lack of massive amounts of
labeled data, domain adaptation adapt the feature generating model to
another feature domain so that it improve the performance when dealing
with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} proposed to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabled video imagery.
